### 2021-09-09 README.Rmd
{targets}ification

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)
```

@@

### Note on "corrupt caterpillar" project name

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)
```

@@

### `r emoji_glue(":devil::bug:")`: Note on "corrupt caterpillar" project name
